PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-05-30 qfenv_paper/qf_environment.tex
Minor changes

\section{Summary} \label{sec:summary}
Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$. Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the quiescent fraction in low density environments. While the difference in quiescent fraction between the two environments is significant, it remains constant throughout the redshift range suggesting that the evolution of the quiescent fraction is independent of environment.

>>>>

\section{Summary} \label{sec:summary}
Using a stellar mass complete galaxy sample, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$. Furthermore with a consistently measured galaxy environment from robust spectroscopic redshift, we demonstrate that the quiescent fraction in high density environments is always greater than the fraction in low density environments. While the difference in quiescent fraction between the two environments is significant, it remains constant throughout the redshift range suggesting that the evolution of the quiescent fraction is independent of environment.
